Battling Climate Change: Implications on the Canadian Climate Policies in Recent Years

### 2022-04-27 outputs/paper/paper.Rmd
Added additional information to appendix

>>>>

# GHG emission levels for different economic sectors in Canada
```{r, echo=FALSE, warning=FALSE,message=FALSE}
sector_ghg_emissions <- read_csv("../../inputs/data/ghg-emissions-sector-en.csv", 
                                    skip = 1)
sector_ghg_emissions <- sector_ghg_emissions[1:32,]
colnames(sector_ghg_emissions) <- sector_ghg_emissions[1,]
sector_ghg_emissions <- sector_ghg_emissions[-1, ] 
colnames(sector_ghg_emissions) <- c("Year", "Oil and gas", "Transport", "Buildings", "Electricity", "Heavy industry", "Agriculture", "Waste and others")
sector_ghg_emissions <- mutate_all(sector_ghg_emissions, function(x) as.numeric(as.character(x)))
sector_ghg_emissions %>%
  kable(caption = "GHG emission levels for different economic sectors in Canada, in Mt CO2 eq")%>%
  kable_styling(latex_options = "HOLD_position")%>%
  add_header_above()
```

# Canada's GHG emission levels by province and territories
```{r, echo=FALSE, warning=FALSE,message=FALSE}
prov_ghg_emissions <- read_csv("../../inputs/data/ghg-emissions-regional-en.csv", 
                                      skip = 1)
prov_ghg_emissions <- prov_ghg_emissions[1:14,]
colnames(prov_ghg_emissions) <- prov_ghg_emissions[1,]
prov_ghg_emissions <- prov_ghg_emissions[-1, ]

colnames(prov_ghg_emissions) <- c("Province or Territory", "1990 GHG Emissions", "2005 GHG Emissions", "2020 GHG Emissions")

prov_ghg_emissions%>%
  kable(caption = "Canada's GHG emission levels by province or territory, in Mt CO2 eq")%>%
  kable_styling(latex_options = "HOLD_position")%>%
  add_header_above()
```
